Evolving New State-of-the-Art for Voronoi Diagram and Distance Transform From JFA Using AutoML

### 2020-09-19 paper/main.tex
new abstract

\hl{\textbf{UWAGA}: wymyslic prawidlowa nazwe pracy + poprawic zlozonosci +
opisac dwa algorytmy}

\begin{abstract}
This paper studies a practical usage of machine learning (AutoML) to automate
research towards discovering efficient Voronoi Diagram and Distance
Transform algorithms.  As the baseline we used the Jump Flooding Algorithm
(JFA) - by finding new mutations which works best for specific data, and
then ensembling them into one, we create new state-of-the-art algorithm in
this field named \textbf{\ourjfa} \hspace{0.01cm} with best-case
\textcolor{red}{$O(1)$} time complexity and \textcolor{red}{$O(N)$} work
complexity - in addition, we introduce \textbf{\ourjfasingle}, a single
variant that in most cases outperforms original JFA with proven worst-case
\textcolor{red}{$O(\log^{*}N)$} time complexity.
The algorithm is faster and produces more accurate approximations. It could be
extended into 3D space in a slice-by-slice manner.  We started from the
assumption that JFA has potential for improvement - some benefits can be
observed for specific data by adding random noise and adjusting the step size in
JFA.  This showed us that, AutoML could examine this space, and find the best
possible algorithm in each case.  In the further part of the work, we discuss
the results, compare the variants and ensemble for creating the final algorithm.
\end{abstract}

@@

Based on this research and findings, several efficient GPU-based algorithms which are either
work optimal or time optimal have been proposed including
SKW \cite{schneider2009gpu}, PBA \cite{cao2010parallel}, FastGPU \cite{de2017fast}, Honda's algorithm \cite{honda2017simple} and
WTO \cite{manduhu2019work}.

The main question that needs to be addressed now is whether JFA has potential
for improvement. We found some benefits for specific data by adding random noise
and adjusting the phase size in JFA. Therefore, this shows that, AutoML could examine this
unknown space, and find the best possible algorithm in each case.

@@

\begin{enumerate}
	\item Presenting new state-of-the-art variants of algorithm for Voronoi
		Diagram and Distance Transform: \newline
		\textbf{\ourjfasingle} - (Multi-domain) single variant;
		\textbf{\ourjfa} - (Specific-domain) ensemble of weak variants; and
	\item Analyzing all possible variants of JFA: comparing error and speedup
		relative to bruteforce method
%\item Proposing, for an input set of seeds in a 2D grid, the first
%parallel algorithm in GPU to compute in constant time (i.e.
%independent of the number of seeds) a highly accurate
%Voronoi diagram and distance transform.
\end{enumerate}

@@

\begin{table}[H] \centering
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Reference}                & \textbf{Algorithm}    & \textbf{Exactness}
	& \textbf{Time}         & \textbf{Work}         \\ \midrule
\citep{de2017fast}       & FastGPU      & Exact       & $O(n^3/p)$   & -            \\
\citep{cao2010parallel}  & PBA          & Exact       & $O(n)$       & $O(mN)$      \\
\citep{honda2017simple}  & based on SKW & Exact       & $O(n)$       & $O(N)$       \\
\citep{manduhu2019work}  & WTO          & \cellcolor{blue!25}\textbf{Exact}&
	\cellcolor{blue!25}$\mathbf{O(\log n)}$  & $O(N)$       \\
\citep{schneider2009gpu} & SKW          & Approximate & $O(n)$       & $O(N)$       \\
\citep{rong2006jump}     & JFA          & Approximate & $O(\log n)$  & $O(N\log n)$ \\ \bottomrule
In this paper            & \ourjfasingle&
	\cellcolor{blue!25}\textbf{Approximate} &
	\cellcolor{blue!25}$\sim$$\mathbf{O(\log^{\ast} n)}$ & $\sim$$O(N)$ \\
                         & \ourjfa      &
	\cellcolor{blue!25}\textbf{Approximate} &
	\cellcolor{blue!25}$\sim$$\mathbf{O(1)}$ & $\sim$$O(N)$ \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Different GPU algorithms for computing EDT}
\end{table}

@@

\subsection{Specific-domain Algorithm} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%\hl{\textbf{UWAGA}: wymyslic prawidlowa nazwe pracy + poprawic zlozonosci +
%opisac dwa algorytmy}

\begin{abstract}
This paper studies a practical usage of machine learning (AutoML) to automate
research towards discovering efficient Voronoi Diagram and Distance
Transform algorithms.  As the baseline we used the Jump Flooding Algorithm
(JFA) - by finding new mutations which works best for specific data, and
then ensembling them into one, we create new state-of-the-art algorithm in
this field named \textbf{\ourjfa} with best-case
\textcolor{red}{$O(1)$} time complexity and \textcolor{red}{$O(N)$} work
complexity - in addition, we introduce \textbf{\ourjfasingle}, a single
variant that in most cases outperforms original JFA with proven worst-case
\textcolor{red}{$O(\log^{*}N)$} time complexity.
The algorithm is faster and produces more accurate approximations. It could be
extended into 3D space in a slice-by-slice manner.  We started from the
assumption that JFA has potential for improvement - some benefits can be
observed for specific data by adding random noise and adjusting the step size in
JFA.  This showed us that, AutoML could examine this space, and find the best
possible algorithm in each case.  In the further part of the work, we discuss
the results, compare the variants and ensemble for creating the final algorithm.
\end{abstract}

@@

Based on this research and findings, several efficient GPU-based algorithms which are either
work optimal or time optimal have been proposed including
SKW \cite{schneider2009gpu}, PBA \cite{cao2010parallel}, FastGPU \cite{de2017fast}, Honda's algorithm \cite{honda2017simple} and
WTO \cite{manduhu2019work}.
% XXX
The main question that needs to be addressed is whether JFA has potential
for improvement. We found some benefits for specific data by adding random noise
and adjusting the phase size in JFA. Therefore, this shows that, AutoML could examine this
unknown space, and find the best possible algorithm in each case.

@@

\begin{enumerate}
	\item Presenting new envolved state-of-the-art variants of algorithm for Voronoi
		Diagram and Distance Transform: % \newline
		\textbf{\ourjfasingle} - (Multi-domain) single variant, replacement of JFA;
		\textbf{\ourjfa} - (Ensemble of Domain-specific) multiple weak variants, production ready; and
	\item Analyzing all possible variants of JFA: comparing error and speedup
		relative to bruteforce method in different domains.
%\item Proposing, for an input set of seeds in a 2D grid, the first
%parallel algorithm in GPU to compute in constant time (i.e.
%independent of the number of seeds) a highly accurate
%Voronoi diagram and distance transform.
\end{enumerate}

\hl{czy (Ensemble of Domain-specific) weak variants - jest prawidlowo?}

@@

\begin{table}[H] \centering
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Reference}                & \textbf{Algorithm}    & \textbf{Exactness}
	& \textbf{Time}         & \textbf{Work}         \\ \midrule
\citep{de2017fast}       & FastGPU      & Exact       & $O(n^3/p)$   & -            \\
\citep{cao2010parallel}  & PBA          & Exact       & $O(n)$       & $O(mN)$      \\
\citep{honda2017simple}  & based on SKW & Exact       & $O(n)$       & $O(N)$       \\
\citep{manduhu2019work}  & WTO          & \cellcolor{blue!25}\textbf{Exact}&
	\cellcolor{blue!25}$\mathbf{O(\log n)}$  & $O(N)$       \\
\citep{schneider2009gpu} & SKW          & Approximate & $O(n)$       & $O(N)$       \\
\citep{rong2006jump}     & JFA          & Approximate & $O(\log n)$  & $O(N\log n)$ \\ \bottomrule
In this paper            & \ourjfasingle&
	\cellcolor{blue!25}\textbf{Approximate} &
	\cellcolor{blue!25}$\sim$$\mathbf{O(\log^{\ast} n)}$ & $\sim$$O(N\log^{\ast} n)$ \\
                         & \ourjfa      &
	\cellcolor{blue!25}\textbf{Approximate} &
	\cellcolor{blue!25}$\sim$$\mathbf{O(1)}$ & $\sim$$O(N)$ \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Different GPU algorithms for computing EDT}
\end{table}

@@

\subsection{Domain-specific Algorithms} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
